Inverse Modular Reinforcement Learning on Human Motion

### 2015-02-11 paper.tex
exp results in

@@

Consider the task illustrated in Figure~\ref{fig:avatar} A). The avatar is asked to
do three sub-tasks simultaneously --- 1) following the path, indicated by the gray
line on the ground, 2) getting targets, the blue cylinders, and 3) avoiding
obstacles, the pink cylinders \cite{rothkopf2013modular}.

@@

@@

We conducted experiments to ask volunteers to accomplish different tasks and
recorded their trajectories. There are four kind of tasks. Task 1, following the
path only, and ignoring other objects. Task 2, following the path, while avoid
the obstacles. Task 3, following the path, while attain targets when possible.
Task 4, following the path, collecting the targets and avoiding obstacles
simutanously.

@@

From a different perspective, can we find a weight vector to best interpret
human's behavior. In Figure~\ref{fig:exp}, same as Figure~\ref{fig:avatar}, the
red circles are obstacles. The blue circles are targets. The gray line is the
path. The black lines are trajectories of human . The left figure shows the case
where human follows the path and ignores the targets and obstacles. The right
figure shows the case that human does three sub-tasks simultaneously. The human
data are collected by the Center for Perceptual Systems in University of Texas
at Austin.

We make some constraints on our learning agent to make it behavior like humans.
It is allowed to go straight ahead, turn left with a small step, or turn right
with a small step.

Now, we assume a learning agent that only knows the three sub-MDPs and the human
data. It looks at the human behavior, and finds the weights that can interpret
such behavior. Using such weights, the trajectories of our agents are drawn in
the green lines. We can tell that in the left figure, the agent puts a large
weight on path-following. In the right figure, it puts weights on all sub-MDPs.

@@

\begin{table}[h]
\centering
\begin{tabular}{| l| l| l |}
\hline
Average by Task & Num Targs Hit & Num Obst Hit\\
\hline
1 & 2.34 &  2.13\\
\hline
2 & 3.03 &  0.13\\
\hline
3 & 10.19 & 2.28\\
\hline
4 & 9.88 &  0.03\\
\hline
\end{tabular}
\caption{Number of targets hit and number of obstacles hit for human's behavior.}
\end{table}

@@

Weighted sum of Q function is one way to combine multiple sub-MDPs. We also
propose other ways, for example, scheduling between different modules, with only
one active at one time. However, when a human tries to collect targets while
avoiding obstacles, these two modules should be both on. A scheduling approach
may yield frequent oscination between target and obstacle modules.

>>>>

We conduct this research motivated by two questions.

@@

Consider the task illustrated in Figure~\ref{fig:avatar} A). The avatar is asked to
do three sub-tasks simultaneously --- 1) following the path, indicated by the gray
line on the ground, 2) getting targets, the blue cylinders, and 3) avoiding
obstacles, the pink cylinders. This is an experiment design used in the
literature to evaluate modular reinforcement learning \cite{rothkopf2013modular}.

@@

To obtain the weights given the samples, we need to use the Inverse Modular
Reinforcement Learning technique \cite{rothkopf2013modular}.

@@

We conducted experiments to ask volunteers to accomplish different tasks and
recorded their trajectories. There are four kind of tasks. Task 1, following the
path only, and ignoring other objects. Task 2, following the path, while avoid
the obstacles. Task 3, following the path, while attain targets when possible.
Task 4, following the path, collecting the targets and avoiding obstacles
simutanously.
The human data are collected by the Center for Perceptual Systems in University
of Texas at Austin.

@@

From a different perspective, can we find a weight vector to best interpret
human's behavior. In Figure~\ref{fig:exp}, same as Figure~\ref{fig:avatar}, the
red circles are obstacles. The blue circles are targets. The gray line is the
path. The black lines are trajectories of human.
%TODO

We make some constraints on our learning agent to make it walk like a human.
We can find in the human trajectories that humans walk smoothly. They don't turn
sharply.  Our agent is allowed to do three actions --- going straight ahead,
turning left with a small step, and turning right with a small step.

To make our weights represent the significance of the modules, we
normalize the sub-MDPs with the unit (positive or negative) rewards. The reward
is 1 for collecting a target, -1 for running into an obstacle. We define the
value function directly for the path module to have a path following performance.

The agent only considers the closest target and the closest obstacle.

We assume that our learning agent only knows the three sub-MDPs and the human
data. It looks at the human behavior, and finds the weights that can interpret
such behavior. 
Using such weights, the trajectories of our agents are drawn in the green lines.
We can tell that in the left figure, the agent puts a large weight on
path-following.  In the right figure, it puts weights on all sub-MDPs.

@@

\begin{table}[h]
\centering
\begin{tabular}{| l| l| l |}
\hline
Average by Task & Num Targs Hit & Num Obst Hit\\
\hline
1 & 2.34 &  2.13\\
\hline
2 & 3.03 &  \bf{0.13}\\
\hline
3 & \bf{10.19} & 2.28\\
\hline
4 & \bf{9.88} &  \bf{0.03}\\
\hline
\end{tabular}
\caption{Number of targets hit and number of obstacles hit of human.}
\end{table}

\begin{table}[h]
\centering
\begin{tabular}{| l| l| l |}
\hline
Average by Task & Num Targs Hit & Num Obst Hit\\
\hline
1 & 1.25 & 1.62\\
\hline
2 & 3.62 & \bf{2.37}\\
\hline
3 & \bf{5.14} & 3.14\\
\hline
4 & \bf{5.00} & \bf{2.00}\\
\hline
\end{tabular}
\caption{Number of targets hit and number of obstacles hit of the learning agent.}
\end{table}

@@

Weighted sum of Q function is one way to combine multiple sub-MDPs. We also
propose other ways including, for example, scheduling between different modules,
with only one active at one time. However, we adopt the weighted sum approach
because this is more reasonble for human behavior. When a human tries to collect
targets while avoiding obstacles, these two modules are expected to be both
active. A scheduling approach may yield frequent oscination between these two
modules.

We also assumes independency between modules. Correlation between modules
doesn't impair our analysis in this paper. In Figure~\ref{fig:heatmap}, we can
find that the target module and obstacle module tends to be negatively
correlated.
